FoRTE baseline

### 2019-03-27 analysis/paper/paper.Rmd
Order LAI ensemble plots by NPP

annual_lai_workflows_cap <- paste(
  "Max annual leaf area index predictions by plant functional type",
  "across different parameter combinations."
)
```

>>>>

annual_lai_workflows_cap <- paste(
  "Max annual leaf area index predictions by plant functional type",
  "across different parameter combinations.",
  "Facets are arranged in order of increasing mean annual NPP",
  "after 1940."
)
```
